---
title: "Tutorial week 3"
format: html
editor: visual
---

# Reading Avian Influenza Data

```{r read data}
#| echo: false
#| warning: false
#| message: false

library(tidyverse)
dat <- read_csv("data/avian_influenza_numbers.csv")
```

```{r use function head}
#| echo: false
#| output: false
head(dat, 10)
glimpse(dat)
str(dat)
#show data structure ex. class
```

The dataset has `r nrow(dat)` rows and `r ncol(dat)` columns.

The dataset has `{r} nrow(dat)` rows and `{r} ncol(dat)` columns.
Return the same results

### Why is it important to know the dimension of your dataset?
To have a better understanding of the data, verify you results, and determine the complexity of your analysis / model.

### What are the variable names in the dataset?
```{r}
names(dat)
```

- Month: The particular month that the infection is recorded.
- China: The number of cases recorded in each month.

## Exercise 4

```{r}
library(lubridate)
data_clean <- dat |> 
  select(Month, Australia, Egypt, `United States`) |> 
  mutate(Month = mdy(Month)) |> 
  filter(!is.na(Month))
## United states has space so `` is needed
```

```{r}
library(kableExtra)
data_clean |> 
  summarise(count_aus = sum(Australia),
            count_egy = sum(Egypt), 
            count_us = sum(`United States`) 
            ) |> 
  kable() |> 
  kable_styling()
```

Visualise the counts using histogram
```{r}
library(ggplot2)

#plot one country at a time
data_clean |> 
  ggplot(aes(x = Egypt)) + 
  geom_histogram(binwidth = 5)

#plot multiple countries at the same time
data_clean |> 
  pivot_longer(-Month) |> 
  ggplot(aes(x = value, fill = name)) + 
  geom_histogram(binwidth = 5, position = "dodge") + 
  facet_wrap(~name)

#do not change Month column
  
```


